---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r}
#| label: setup
#| include: false

knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# MultiStateTMLE

<!-- badges: start -->
[![R-CMD-check](https://github.com/BjarkeHautop/MultiStateTMLE/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/BjarkeHautop/MultiStateTMLE/actions/workflows/R-CMD-check.yaml)
[![Codecov test
coverage](https://codecov.io/gh/BjarkeHautop/MultiStateTMLE/graph/badge.svg)](https://app.codecov.io/gh/BjarkeHautop/MultiStateTMLE)
<!-- badges: end -->

MultiStateTMLE is a framework for nonparametric causal inference with multistate
event processes, built around stochastic intensity interventions, calibrated
interventions, and composite estimands, and estimated using targeted maximum
likelihood estimation (TMLE) allowing flexible nuisance learning.

## Installation

You can install the development version of MultiStateTMLE from
[GitHub](https://github.com/) with:

```r
# install.packages("pak")
pak::pak("BjarkeHautop/MultiStateTMLE")
```

## Usage

```{r}
#| label: example

library(MultiStateTMLE)
```

The pipeline has three main steps:

- `prepare.initial()` fits the initial (nuisance) hazard models for each process
  in the data (Cox, HAL, or exponential), and builds the discrete product state
  space used internally.
- `tmle.alpha.fun()` targets the initial fit under a stochastic intensity
  intervention (scaling the shape of a process by `alpha`, optionally combined
  with an intervention on baseline treatment), returning a TMLE estimate, its
  standard error, and (optionally) the efficient influence curve.
- `calibration.fun()`/`calibration.curve.fun()` calibrate the shape intervention
  to a target effect size, and `make.calibrated.contrasts()` decomposes a total
  treatment effect into mediated and calibrated contrasts.

`sim.generic()` and `sim.from.data()` (built on top of
[simevent](https://github.com/BjarkeHautop/simevent)) simulate multistate event
history data, either from a user-specified process/effect specification, or from
parameters previously fitted to observed data.

## Contributing

All contributions are welcome!
